### 2024-02-19 sections/5classification.tex
Add files via upload

\begin{observation}\label{obs:explore_D*}
    For the purposes of the observation we will shorten notation to $\mathscr{D}_* := \disk (\mathsf{D}_{0 \subset n}^*)$. Since the defect is a point there can be at most one disk that contains it per morphism. Thus, the morphism spaces to consider are
    %
    \begin{align}
        &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n),& &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n_*)& &\mathrm{and}& &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*).&
    \end{align}
    %
    The first of these is equivalent to the space $\mathsf{Emb}^*((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n)$ of framed open embeddings, which makes it is obvious that restricting to non-defect disks would give the data of an $\mathbb{E}_n$-algebra. This is related to \cref{lem:ff_functor_to_refinement}, which says that forgetting the stratification results in obtaining a full $\infty$-subcategory of locally constant factorization algebras. When $i=0$, the third space above is equivalent to a point, which makes it clear that restricting exclusively to pointed disks $\mathbb{R}^n_*$ would give rise to plain objects\footnote{We've omitted mentioning the fact that, because of morphisms like $\emptyset \xrightarrow{} U$, all of the above algebraic objects will be pointed. We have done this to avoid confusion with the use of pointed in the sense of a point defect of the space.} (or $\mathbb{E}_0$-algebras). The structure that connects these two algebras is encoded in the rest of the morphism spaces. In fact the second and third space above are equivalent,
    %
    \begin{equation}
        \mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n_*) \simeq \mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*) \simeq \mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\}),
    \end{equation}
    %
    for all $i \in \mathbb{N}$, where $\mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\})$ is the space of framed embeddings of $i$ $n$-dimensional disks into the punctured $\mathbb{R}^n$.

    All of this is an elaboration of the fact that $\mathsf{D}_{0 \subset n}^*$ is equivalent to $\Delta^1 = \{0 \xrightarrow{} 1\}$ as $\infty$-categories (saying nothing about the right fibration to $\bsc$). Namely, the only nontrivial morphism is

>>>>

\begin{observation}\label{obs:explore_D*}
    For the purposes of the observation we will shorten notation to $\mathscr{D}_* := \disk (\mathsf{D}_{0 \subset n}^*)$. Since the defect is a point there can be at most one disk that contains it per morphism. Thus, the morphism spaces to consider are
    %
    \begin{align}
        &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n),& &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n_*)& &\mathrm{and}& &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*).&
    \end{align}
    %
    The first of these is equivalent to the space $\mathsf{Emb}^*((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n)$ of framed open embeddings, which makes it is obvious that restricting to non-defect disks would give the data of an $\mathbb{E}_n$-algebra. This is related to \cref{lem:ff_functor_to_refinement}, which says that forgetting the stratification results in obtaining a full $\infty$-subcategory of locally constant factorization algebras. When $i=0$, the third space above is equivalent to a point, which makes it clear that restricting exclusively to pointed disks $\mathbb{R}^n_*$ would give rise to plain objects\footnote{We've omitted mentioning the fact that, because of morphisms like $\emptyset \xrightarrow{} U$, all of the above algebraic objects will be pointed. We have done this to avoid confusion with the use of pointed in the sense of a point defect of the space.} (or $\mathbb{E}_0$-algebras). The structure that connects these two algebras is encoded in the rest of the morphism spaces. In fact the second and third space above are equivalent,
    %
    \begin{equation}
        \mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n_*) \simeq \mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*) \simeq \mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\}),
    \end{equation}
    %
    for all $i \in \mathbb{N}$, where $\mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\})$ is the space of framed embeddings of $i$ $n$-dimensional disks into the punctured $\mathbb{R}^n$. All of these facts are partially an elaboration of the fact that $\mathsf{D}_{0 \subset n}^*$ is equivalent to $\Delta^1 = \{0 \xrightarrow{} 1\}$ as $\infty$-categories (saying nothing about the right fibration to $\bsc$).
